\section{Very Short Overview}

\subsection{Agency}

\begin{enumerate}
    \item Ask: is the principal liable to a third party for another's actions?
    \item An \textbf{agency relationship} requires the principal's 
    \textbf{assent}, that the agent acts on the principal's \textbf{behalf}, 
    that the agent is subject to the principal's \textbf{control}, and that 
    the agent \textbf{consents} to so act. Restatement (Third) \S\ 1.01.
    \item Agency exists in \textbf{contract} if:
    \begin{enumerate}
        \item The agent has \textbf{authority}:
        \begin{enumerate}
            \item \textbf{Actual}.
            \item \textbf{Implied}.
            \item \textbf{Apparent}.
        \end{enumerate}
        \item Or, an exception applies:
        \begin{enumerate}
            \item \textbf{Ratification}.
            \item \textbf{Estoppel}.
            \item \textbf{Undisclosed principal}.
        \end{enumerate}
    \end{enumerate}
    \item Agency exists in \textbf{tort} under \textbf{respondeat superior} 
    if:
    \begin{enumerate}
        \item The agent is \textbf{employee} acting within the \textbf{scope 
        of employement}; or
        \item The agent acts with \textbf{apparent authority}.
        \item \textbf{Franchises} \emph{may} establish an employee 
        relationship.
    \end{enumerate}
    \item \textbf{Agent's liability}.
    \item \textbf{Agent's fiduciary duties}.
    \item \textbf{Strategies} for avoiding liability.
\end{enumerate}

\newpage

\subsection{Partnership}

\begin{enumerate}
    \item \textbf{Who and what}:
    \begin{enumerate}
        \item ``The association of two or more persons to carry on as 
        co-owners a business for profit forms a partnership, whether or not 
        the persons intended to form a partnership.'' RUPA \S\ 202(a)
        \item \textbf{Intent} is not determinative.
        \item \textbf{Joint and several liability}.
        \item Partnership by \textbf{estoppel}.
    \end{enumerate}
    \item \textbf{Fiduciary duties}: duty to \textbf{share partnership 
    opportunities}. RUPA \S\ 404.
    \item \textbf{Rights of partners}:
    \begin{enumerate}
        \item All partners are \textbf{agents}.
        \item Changing the partnership structure requires a \textbf{majority 
        vote}.
    \end{enumerate}
\end{enumerate}

\newpage

\subsection{Corporate Formation}

\begin{enumerate}
    \item \textbf{Corporate structure}.
    \begin{enumerate}
        \item \textbf{Public} vs. \textbf{private/closely held}.
        \item \textbf{Dividends}.
    \end{enumerate}
    \item \textbf{Formation}.
    \begin{enumerate}
        \item \textbf{Articles of incorporation}.
        \item \textbf{Capital structure} (authorized shares).
        \item \textbf{Organizational consent}: bylaws, officers, other 
        business.
        \item \textbf{Bylaws}.
        \item \textbf{Officer appointments}.
        \item \textbf{Stock issuance} (subscription, issuance).
        \item \textbf{Shareholders' agreement}.
        \item \textbf{Annual elections}.
    \end{enumerate}
    \item \textbf{Limited liability}.
    \begin{enumerate}
        \item \textbf{Enterprise liability}: commingling sisters.
        \item \textbf{Piercing the corporate veil}: sloppiness or injustice.
        \item \textbf{Dividend rules}: pay creditors; personal director 
        liability for impermissible dividends.
        \item \textbf{Reverse piercing}.
    \end{enumerate}
    \item \textbf{Role and purpose of the corporation}.
    \begin{enumerate}
        \item ``Henry Ford'' problem: philanthropy.
    \end{enumerate}
\end{enumerate}

\newpage

\subsection{Limited Liability Company}

\begin{enumerate}
    \item \textbf{Limited partnership}: limited/passive vs. general/active.
    \item \textbf{Limited liability partnership}: extra liability limitations 
    for professional services.
    \item \textbf{Limited liability companany}:
    \begin{enumerate}
        \item \textbf{Overview}:
        \begin{enumerate}
            \item Flow-through taxation.
            \item Compare to s-corp (100 shareholders, no preferred stock, 
            entities can't own shares).
            \item Formation: articles of organization, operating agreement.
            \item Membership
            \item Management: member-managed vs. manager-managed.
            \item Transferability: easy to transfer economic interest but not 
            membership interest.
            \item Limited liability under ULLCA \S\ 303(a), but veil can be 
            pierced---see below.
        \end{enumerate}
        \item \textbf{Operating agreements}: member- or manager-managed, 
        management rights, which members are agents.
        \item \textbf{Piercing the LLC veil}: unity of interest and ownership 
        (lack of formalities, commingling, under-capitalization), injustice 
        (fraud-like conduct, unjust enrichment).
        \item \textbf{Fiduciary duties}: managers have duties of loyalty and 
        care; members don't have duties if they are not managers.
    \end{enumerate}
\end{enumerate}

\newpage

\subsection{Board of Directors}

\begin{enumerate}
    \item \textbf{Business judgment rule} applies unless:
    \begin{enumerate}
        \item The board was \textbf{grossly negligent in becoming informed} (duty of care) or 
        \item Board acted with \textbf{bad faith} or engaged in 
        \textbf{self-dealing} (duty of loyalty).
    \end{enumerate}
    \item Under the BJR, courts will \textbf{defer} to the board's decision 
    unless it was \textbf{irrational or constituted waste}.
    \item \textbf{Duty of care}:
    \begin{enumerate}
        \item Directors must act with diligence of reasonable person under 
        similar circumstances.
        \item Rebutting BJR: board was \textbf{grossly negligent in becoming 
        informed}. \emph{Van Gorkom}.
        \item Articles can \textbf{eliminate personal liability} for breaches 
        of duty of care (but not loyalty or good faith). DGCL \S\ 102(b)(7).
    \end{enumerate}
    \item \textbf{Duty of loyalty}:
    \begin{enumerate}
        \item \textbf{Directors' and managers' conflicts}: Self-dealing 
        transaction can be cleansed with (1) majority all of disinterested 
        directors, (2) majority\footnote{But see \emph{Fliegler}, apparently 
        only requiring majority of \emph{disinterested} shareholders.} of 
        shareholders, or (3) entire fairness (using the \emph{Beran} factors).
        \item \textbf{Corporate opportunity} exists if it passes the 
        \emph{Broz} test: (1) financial capability, (2) line of business, (3) 
        interest or expectancy, (4) resulting conflicts.
        \item \textbf{Dominant shareholder}: intrinsic fairness (essentially, 
        entire fairness) applies when a dominant shareholder \textbf{engages 
        in self-dealing}---i.e., when the dominant shareholder receives 
        something ``to the exclusion of, and detriment to, the minority 
        stockholders'' of the corporation (often, a subsidiary).  
        \emph{Sinclair Oil v. Levien}.
        \item \textbf{Voting}:
        \begin{enumerate}
            \item Proposed resolutions vs. UWCs---see drafting exercises.
            \item Two voting standards: general and mergers.
            \item Articles or bylaws can override statutory meeting notice 
            rules. MBCA \S\ 8.22.
            \item Shareholders' written consent rule \textbf{trumps bylaws}. 
            MBCA \S\ 7.04(a). 
        \end{enumerate}
    \end{enumerate}
    \item \textbf{Good faith}: overcompensation and oversight.
    \item See ``director fiduciary duty'' chart.
\end{enumerate}

\newpage

\subsection{Advising Choice of Entity}

\begin{enumerate}
    \item See charts in overview.
\end{enumerate}

\newpage

\subsection{Securities}

\begin{enumerate}
    \item \textbf{Security}: stock, specific instrument, ``investment 
    contract.''
    \item Corporate stock is \textbf{always a security}.
    \item \textbf{'33 Act}:
    \begin{enumerate}
        \item \textbf{Transactions} on the \textbf{primary market}.
        \item \S\ Requires \textbf{registration} of an offer or sale unless an 
        \textbf{exemption} applies. Applies to sale to raise capital or 
        issuance as part of a merger or acquisition.
        \item Goals: \textbf{mandate disclosure} and \textbf{prevent fraud}.
        \item \textbf{Public offering}: requires \textbf{prospectus} 
        (information to investors) and \textbf{registration statement} (to the 
        SEC).
        \item \textbf{Exemptions}:
        \begin{enumerate}
            \item \textbf{Private placement exemption}, \S\ 4(2), applies to 
            transactions not involving public offerings. Defendants must show 
            (1) \textbf{actual disclosure} to investors or (2) that investors 
            had \textbf{effective access to all pertinent facts}. \emph{Doran 
            v. Petroleum}.
            \item Exempt securities are rare compared to exempt transactions.
            \item \textbf{Remedy}: rescission.
        \end{enumerate}
    \end{enumerate}
    \item \textbf{'34 Act}: governs securities \textbf{markets}.
    \item \textbf{Rule 506} creates a \textbf{safe harbor} for private 
    offerings.
    \item \textbf{Insider trading}:
    \begin{enumerate}
        \item \textbf{Common law fraud}: false representation to induce 
        reliance, actual reliance, damages.
        \item \textbf{Rule 10b-5}:
        \begin{enumerate}
            \item Outlaws deceptive practices.
            \item Goal is to subject all investors to \textbf{identical market 
            risks}.
            \item Those who have inside information must \textbf{disclose} or 
            \textbf{refrain from investing}.
            \item Two theories of fraud: \textbf{classical} (insider breaches 
            a duty) and \textbf{misappropriation} (trusted outsider breaches a 
            duty).
        \end{enumerate} 
    \end{enumerate}
\end{enumerate}

\newpage

\subsection{Public Company Governance}

\begin{enumerate}
    \item \textbf{Proxies}:
    \begin{enumerate}
        \item Shareholders can designate incumbents to act as their proxies.
        \item \textbf{Proxy fights}:
        \begin{enumerate}
            \item Incumbents announce the meeting and solicit proxies as usual.
            \item Insurgents may try to insert \textbf{shareholder proposals} 
            in the company's proxy statement (see below).
            \item Insurgents might \textbf{solicit their own proxies} by 
            obtaining the shareholder list and mailing their own proxy 
            statements.
        \end{enumerate}
    \end{enumerate}
    \item \textbf{Shareholder inspection rights}:
    \begin{enumerate}
        \item Dissidents want the shareholder lists.
        \item Disputes center on whether the purpose is proper. \textbf{Tender 
        offers} are proper. \textbf{Political and ethical} purposes alone are 
        insufficient.
    \end{enumerate}
    \item \textbf{Shareholder proposals}:
    \begin{enumerate}
        \item Shareholder proposals can appear in the company's proxy 
        statement, subject to certain requirements.
        \item Companies can exclude proposals that are not 
        \textbf{significantly related} to the company's business, but ethical 
        or social significance can be enough.
    \end{enumerate}
\end{enumerate}

\newpage

\subsection{Mergers and Acquisitions}

\begin{enumerate}
    \item \textbf{Two-tiered front-loaded cash tender offer}.
    \item \textbf{\emph{Unocal} test}:
    \begin{enumerate}
        \item \textbf{Triggers}: defensive measures.
        \item \textbf{Test}: motive and proportionality.
    \end{enumerate}
    \item \textbf{\emph{Revlon} test}:
    \begin{enumerate}
        \item \textbf{Triggers}: actions that make the break-up of the company 
        inevitable---e.g., self-initiated sale for \textbf{cash} (but not 
        stock), stock-for-stock deal resulting in \textbf{controlling 
        shareholder}, or a \textbf{white knight} deal.
        \item \textbf{Not triggers}: refusal of unsolicited offer; deal where 
        control remains in \textbf{unaffiliated hands} (i.e., the market).
        \item \textbf{Test}: maximize the short term value of the company.
    \end{enumerate}
\end{enumerate}

\newpage

\subsection{Corporate Litigation}

\begin{enumerate}
    \item \textbf{Direct} vs. \textbf{derivative} claims.
    \item Bringing a derivative suit in Delaware: see chart.
    \item Indemnification agreements \textbf{cannot bypass statutory 
    requirements}. \emph{Waltuch}.
    \item Corporations can be required to advance expenses even when the 
    corporation is the plaintiff. \emph{Citadel}.
    \item See the chart on indemnification.
\end{enumerate}

\newpage

\subsection{Close Corporations}

\begin{enumerate}
    \item \textbf{Definition}: (1) small number of shareholders, (2) illiquid 
    stock, and (3) majority of shareholders participate in management. 
    \item \textbf{Control in close corporations}:
    \begin{enumerate}
        \item \textbf{Shareholder voting agreement} (and enforceability---see 
        \emph{Ringling}).
        \item \textbf{Straight voting} vs. \textbf{cumulative voting}.
        \item Limitations on agreements unless they are unanimous. 
        \emph{McQuade, Clark}.
    \end{enumerate}
    \item \textbf{Abuse of control}:
    \begin{enumerate}
        \item Shareholders in close corporations have \textbf{partner duties}. 
        \emph{Donahue}.
        \item \emph{Wilkes} test: (1) legitimate business purpose, (2) less 
        harmful way.
    \end{enumerate}
    \item \textbf{Dissolution}: see charts.
\end{enumerate}

\newpage

\subsection{Corporate Debt}

\begin{enumerate}
    \item Three types: individual loans, bank loans, and 
    \textbf{bonds/debentures}.
    \item In \textbf{bond offerings}, the \textbf{indenture} contains 
    contractual terms, and the \textbf{trustee} represents the interests of 
    the public debt holders.
    \item In \textbf{liquidity}, debt is not transferable unless \textbf{all 
    or substantially all assets} are transferred to a single purchaser. 
    \emph{Sharon Steel}.
    \item Courts will not read an \textbf{implied covenant} into an indenture 
    if it would have the effect of adding contractual terms. \emph{MetLife v. 
    Nabisco}.
\end{enumerate}

\newpage

\section{Venture Capital}

\begin{enumerate}
    \item Transactions favoring preferred stockholders can satisfy entire 
    fairness. \emph{Trados}.
    \item California law:
    \begin{enumerate}
        \item Quasi-California corporations.
        \item Cumulative voting in director elections in close corporations.
        \item Separate votes for separate classes of stock for mergers.
        \item Flexible purpose corporations and benefit corporations.
    \end{enumerate}
\end{enumerate}
